---
title       : Vehicle Fault Data
subtitle    : Daimler
author      : John Cotter
job         : Senior Test Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Information Page

The vehicle fault app gives a visual display of vehicle faults found in an actual test fleet. The input data is a csv file of all vehicle faults in the test fleet. A Google Earth KML file can also be downloaded at the bottom to see a visual representation of the data on a map.  Changing the input date range will filter the faults displayed in the plots and recalculates the output data.

``` {r setOptions, echo=FALSE, results='hide',message=FALSE}
# Set up code for the rest of the presentation
library(googleVis)
library(shiny)
op <- options(gvis.plot.tag = "chart")
ARS327_FTA3_2_RG_Faults_140604_RawData <- read.csv("FaultData/data/ARS327_FTA3_2_RG_Faults_140604_RawData.csv")
faults <- ARS327_FTA3_2_RG_Faults_140604_RawData
```

--- .class #id 

## Faults per Day
Total Faults: 
``` {r echo=FALSE,results='asis',tidy=TRUE} 
nrow(faults) 
```
``` {r CalendarChartPage, echo=FALSE,message=FALSE,warning=FALSE, }
suppressPackageStartupMessages(library(googleVis))
calendarData <- as.data.frame(table(as.Date(faults[,"TIME_STAMP"],"%m/%d/%Y")))
calendarData$Date <- as.POSIXct(calendarData$Var1)
plot(gvisCalendar(calendarData, datevar="Date", numvar="Freq",
        options=list(
          title="Calendar Heat Map",
          height=175
        ),
        chartid="Calendar"
      )
)
#print(Cal, tag='chart')
#cat(createGoogleGadget(Cal), file="CalChart.xml")
#plot(Cal)
```

--- .class #id

## Total Faults

<iframe src="https://johncotter.shinyapps.io/CalendarOnly/" width="100%" 
height="100%" frameborder="0">Loading</iframe>


--- .class #id

## Map of Faults

